Ordinal Tax To Sustain a Digital Economy

### 2019-08-05 writing/short note on digital tax/DigitalTax.tex
more minor changes in the short note.

Until not too long ago, people used to live in relatively self-contained tribes or villages. 
Basic products such as bread or textiles were produced locally. 
Trade primarily existed for specialised products.  
Over time, from the industrial revolution through present technological advancements, more efficient distribution channels have emerged.
Online orders are often delivered within a couple days, independent of a customer’s physical location. 
Extrapolated, this trend leads to an economy where, at least domestically, physical shipping distance becomes irrelevant. 
For digital products and services, this has largely become a reality and contradicts established economic theories, like \cite{Isard1954}'s gravity model of trade which states that trade activity is inversely proportional to physical distance.

To analyse the potential impact of vanishing distance-based transaction costs, we consider the following model economy: 
Two firms offering the same product are competing for a total of $n$ potential buyers. 
Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (Figure \ref{fig:topology}). 
Hence, the maximum distance between any buyer and firm is $d=\ell/2$.

>>>>

Until not too long ago, people used to live in relatively self-contained tribes or villages. 
Basic products such as bread and textiles were produced locally. 
Trade primarily existed for specialised products.  
Over time, from the industrial revolution through present technological advancements in AI, more efficient distribution channels have emerged.
Online orders are often delivered within a couple days, independent of a customer’s physical location. 
Extrapolated, this trend leads to an economy where, at least domestically, physical shipping distance becomes irrelevant. 
For digital products and services, this has largely become a reality and contradicts established economic theories, like \cite{Isard1954}'s gravity model of trade which states that trade activity is inversely proportional to physical distance.

To formally analyse the potential impact of vanishing distance-based transaction costs, we consider the following simple model: 
Two firms offering the same product are competing for a total of $n$ potential buyers. 
Firms and buyers are randomly placed on a one-dimensional ring of length $\ell$ with periodic boundary conditions (Figure \ref{fig:topology}). 
Hence, the maximum distance between any buyer and firm is $d=\ell/2$.
